Title Goes Here

### 2024-04-07 analysis/paper/paper.qmd
update data with state abb for a few schools that were missed, redraw map

total_number_of_ads_in_our_sample <- nrow(jobdata)
```

@@

# get the text in parentheses after the university name that gives the
# state or country abb
uni_state_country <-
jobdata %>%
 select(name_of_hiring_university) %>%
  mutate(state_country = regmatches(name_of_hiring_university,
                                    gregexpr( "(?<=\\().+?(?=\\))",
                                              name_of_hiring_university,
                                              perl = T))) %>%
  unnest(state_country)

@@

# did we get all the job ads?
sum(uni_state_country_tally$n) # 547 most of them, there are 552 ads in our data

@@

>>>>

total_number_of_ads_in_our_sample <- nrow(jobdata) # 550
```

@@

# get the text in parentheses after the university name that gives the
# state or country abb
uni_state_country <- # 550
jobdata %>%  # 550 rows
 select(name_of_hiring_university) %>%
  mutate(state_country = regmatches(name_of_hiring_university,
                                    gregexpr( "(?<=\\().+?(?=\\))",
                                              name_of_hiring_university,
                                              perl = T))) %>%
  unnest(state_country)

@@

# did we get all the job ads?
# sum(uni_state_country_tally$n) # 550 all of them

@@

# how many jobs ads now?
# sum(uni_state_country_tally_us$n) # 433, 78% of the total
